---
title: "CKME 136 - Modelling"
author: "Terry Honner"
date: "July 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#1 - load the libaries, load the data and create the functions

```{r}
rm(list=ls())

library(caret)
library(C50)
library(gbm)
library(glmnet)
library(LogicReg)
library(nnet)
library(rpart)
library(pROC)

masterdata<-read.csv("C:/Users/Chatty Cat Zen/Documents/CKME 136/SP500wk.csv",header = T)

wk_ret_code <- function(wr) (if(wr<=-0.02){"neg"} 
                             else {"neut"})
masterdata$Date<-as.Date(masterdata$Date) # format date

#create a column to lable the type of return
masterdata$wk_ret_code<-0
masterdata$wk_ret_code<-sapply(masterdata$wk_ret,wk_ret_code)
masterdata$wk_ret_code<-as.factor(masterdata$wk_ret_code)

table(masterdata$wk_ret_code) # check results

```
#3 More formatting for splitting the data set

```{r}
#Break up the data into different time series based on the doubling of Price

masterdata$set<-0#create new column to denote the set
masterdata$set[1]<-1
for (i in 2:nrow(masterdata)) 
  ifelse(masterdata$Adj.Close[i]>=masterdata$Adj.Close[1]*2^(masterdata$set[i-1]),
         masterdata$set[i]<-masterdata$set[i-1]+1,
         masterdata$set[i]<-masterdata$set[i-1])


#tail(masterdata$set) #check - values should be 8

#4 Feature Selection

master_ft_select <- subset(masterdata,select=c("w.1","c3","c4","c13","c26","c52","wk_pr_range.1","wk_pr_range.2","wk_pr_range.3","wk_pr_range.4","wk_ret_code","set")) 

test_set<-c(names(master_ft_select))
remove<-c("set")
test_set<-setdiff(test_set,remove)


```
#5 set up training sets based on trajectories
```{r}

#Option 1 - sequenced training

# train1<-master_ft_select[which(master_ft_select$set=="1"),]
# train2<-master_ft_select[which(master_ft_select$set=="2"),]
# train3<-master_ft_select[which(master_ft_select$set=="3"),]
# train4<-master_ft_select[which(master_ft_select$set=="4"),]
# train5<-master_ft_select[which(master_ft_select$set=="5"),]
# train6<-master_ft_select[which(master_ft_select$set=="6"),]
# train7<-master_ft_select[which(master_ft_select$set=="7"),]
# train8<-master_ft_select[which(master_ft_select$set=="8"),]
# 
# mastertest<-master_ft_select[which(master_ft_select$set =="7" | master_ft_select$set=="8"),]
# mastertrain<-master_ft_select[-which(master_ft_select$set =="7" | master_ft_select$set=="8"),]
# 
# test_method<-"sequential"

#*****************************************************************************************************

#Option 2 - Random sets

index <- createDataPartition(masterdata$wk_ret_code, p = 0.7, list = FALSE)
mastertrain <- masterdata[index, ]
mastertest <- masterdata[-index, ]
test_method<-"random"


#******************************************************************************************************

Resultdf<-as.data.frame(matrix(0,ncol=11,nrow=12))
names(Resultdf)<-c("negneg","neutneg","negneut","neutneut","StartTime","EndTime","train_obs","CVfolds","model","AUC","sampling")
i=1

```
#5a Run Model and collect results 
```{r}
#Model A

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)

ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "lda",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


#record results
final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_a <- predict(model, newdata = test_data)
mastertest$pred_a_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_preda_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_preda_neg=predict(model,test_data,type='prob')$neg

i<-i+1
```
#5b Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "rf",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


#record results
final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_b <- predict(model, newdata = test_data)
mastertest$pred_b_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predb_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predb_neg=predict(model,test_data,type='prob')$neg

i=i+1
```
#5c Run Model and collect results 
```{r}



train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "glmnet",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_c <- predict(model, newdata = test_data)
mastertest$pred_c_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predc_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predc_neg=predict(model,test_data,type='prob')$neg


i=i+1
```
#5d Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "treebag",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_d <- predict(model, newdata = test_data)
mastertest$pred_d_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predd_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predd_neg=predict(model,test_data,type='prob')$neg

i = i+1

```

#5e Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "C5.0",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_e <- predict(model, newdata = test_data)
mastertest$pred_e_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_prede_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_prede_neg=predict(model,test_data,type='prob')$neg

i=i+1

```
#5f Run Model and collect results 
```{r}


train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "svmRadial",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_f <- predict(model, newdata = test_data)
mastertest$pred_f_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predf_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predf_neg=predict(model,test_data,type='prob')$neg

i=i+1
```
#5g Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "knn",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_g <- predict(model, newdata = test_data)
mastertest$pred_g_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predg_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predg_neg=predict(model,test_data,type='prob')$neg

i=i+1

```
#5h Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "gbm",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_h <- predict(model, newdata = test_data)
mastertest$pred_h_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predh_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predh_neg=predict(model,test_data,type='prob')$neg

i=i+1

```
#5i Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "rpart",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


#record results
final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_i <- predict(model, newdata = test_data)
mastertest$pred_i_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predi_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predi_neg=predict(model,test_data,type='prob')$neg

i=i+1

```
#5j Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "svmLinear",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


#record results
final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_j <- predict(model, newdata = test_data)
mastertest$pred_j_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predj_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predj_neg=predict(model,test_data,type='prob')$neg

i=i+1

```
#5k Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "nb",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


#record results
final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling

mastertest$pred_k <- predict(model, newdata = test_data)
mastertest$pred_k_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predk_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predk_neg=predict(model,test_data,type='prob')$neg

i=i+1
```


#5l Run Model and collect results 
```{r}

train_data<-subset(mastertrain,select=test_set)
test_data<-subset(mastertest,select=test_set)


#run model 
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10, 
                     savePredictions = 'final',
                     classProbs=T,
                     verboseIter = FALSE,
                     sampling = "down")

Resultdf[i,5]<-Sys.time()  #record the start time of training model to track efficiency

model <- caret::train(wk_ret_code ~ .,
                          data = train_data,
                          method = "nnet",
                         preProcess = c("scale", "center"),
                          trControl = ctrl)

Resultdf[i,6]<-Sys.time()  #record the end time of training model to track efficiency


#record results
final <- data.frame(actual = test_data$wk_ret_code,
                        predict(model, newdata = test_data))

finaltable<-table(final)
Resultdf[i,1]<-finaltable[1,1]
Resultdf[i,2]<-finaltable[1,2]
Resultdf[i,3]<-finaltable[2,1]
Resultdf[i,4]<-finaltable[2,2]
Resultdf[i,7]<-nrow(train_data)
Resultdf[i,8]<-ctrl$number
Resultdf[i,9]<-model$method
Resultdf[i,11]<-ctrl$sampling


mastertest$pred_l <- predict(model, newdata = test_data)
mastertest$pred_l_prob<-predict(model, newdata = test_data,type = 'prob')

mastertrain$OOF_predl_neg=model$pred$neg[order(model$pred$rowIndex)]
mastertest$OOF_predl_neg=predict(model,test_data,type='prob')$neg

i=i+1

```

calculate statistics

```{r}

MCC <- function(TP, TN, FP, FN) {(TP*TN-FP*FN)/(sqrt((TP+FP)*(TP+FN)*(TN+FP)*(TN+FN)))}
temp<-c(Resultdf$negneg,Resultdf$negneut,Resultdf$negneut,Resultdf$neutneg)



Resultdf$testobs<-Resultdf$negneg+Resultdf$neutneg+Resultdf$negneut+Resultdf$neutneut
Resultdf$TP<-Resultdf$negneg+Resultdf$neutneut
Resultdf$Accuracy<-Resultdf$TP/Resultdf$testobs
Resultdf$PRneg<-Resultdf$negneg/(Resultdf$negneg+Resultdf$neutneg)
Resultdf$PRneut<-Resultdf$neutneut/(Resultdf$negneut+Resultdf$neutneut)
Resultdf$Recneg<-Resultdf$negneg/(Resultdf$negneg+Resultdf$negneut)
Resultdf$Recneut<-Resultdf$neutneut/(Resultdf$neutneg+Resultdf$neutneut)
Resultdf$PRtime<-Resultdf$EndTime-Resultdf$StartTime
Resultdf$T_obs_sec<-(Resultdf$train_obs*Resultdf$CVfolds)/Resultdf$PRtime
Resultdf$Actual<-Resultdf$negneg+Resultdf$neutneg
Resultdf$Predicted<-Resultdf$negneg+Resultdf$negneut
Resultdf$F1Score<-2*(Resultdf$PRneg*Resultdf$Recneg)/(Resultdf$PRneg+Resultdf$Recneg)
Resultdf$MCC<-mapply(MCC,Resultdf$negneg,Resultdf$neutneut,Resultdf$negneut,Resultdf$neutneg)

Resultdf[1,10]<-auc(mastertest$wk_ret_code,mastertest$pred_a_prob$neg)
Resultdf[2,10]<-auc(mastertest$wk_ret_code,mastertest$pred_b_prob$neg)
Resultdf[3,10]<-auc(mastertest$wk_ret_code,mastertest$pred_c_prob$neg)
Resultdf[4,10]<-auc(mastertest$wk_ret_code,mastertest$pred_d_prob$neg)
Resultdf[5,10]<-auc(mastertest$wk_ret_code,mastertest$pred_e_prob$neg)
Resultdf[6,10]<-auc(mastertest$wk_ret_code,mastertest$pred_f_prob$neg)
Resultdf[7,10]<-auc(mastertest$wk_ret_code,mastertest$pred_g_prob$neg)
Resultdf[8,10]<-auc(mastertest$wk_ret_code,mastertest$pred_h_prob$neg)
Resultdf[9,10]<-auc(mastertest$wk_ret_code,mastertest$pred_i_prob$neg)
Resultdf[10,10]<-auc(mastertest$wk_ret_code,mastertest$pred_j_prob$neg)
Resultdf[11,10]<-auc(mastertest$wk_ret_code,mastertest$pred_k_prob$neg)
Resultdf[12,10]<-auc(mastertest$wk_ret_code,mastertest$pred_l_prob$neg)


write(test_set,file = "C:/Users/Chatty Cat Zen/Documents/CKME 136/output/modeltest.csv",ncolumns=20)
write(test_method,file = "C:/Users/Chatty Cat Zen/Documents/CKME 136/output/modeltest.csv",sep=",",append = T)
write.table(Resultdf,file = "C:/Users/Chatty Cat Zen/Documents/CKME 136/output/modeltest.csv",sep=",",append = T)

```

